\vspace{-1cm} \bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}

### 2018-03-15 latex/paper.tex
Edits from Brill's thorough critique

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
\usepackage[charter]{mathdesign}
\usepackage[numbers]{natbib}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{lineno}
\usepackage{setspace}
\usepackage{microtype}
\graphicspath{{../figures/}}
\bibliographystyle{unsrtcurrbiol}

@@

% newcommand
\newcommand{\PIP}{PIP\textsubscript{2}}
\newcommand{\sigd}{$\beta$\textit{2t}-SigD}
\newcommand{\sktl}{\textit{sktl}}
\makeatletter
\renewcommand\@biblabel[1]{#1.}
\makeatother

@@

\title{\vspace{-1cm} \bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}}
\author[1,2]{Alind Gupta \thanks{\url{alind.gupta@mail.utoronto.ca}}}
\author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}

\affil[1]{\small Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
\affil[2]{\small Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
\date{\small \today}

@@

\maketitle

@@

    \section{Results}
    Cilia are sensory organelles that are present on almost all cells in the human body
    \citep{satir2010primary, marshall2006cilia}.
    They function in signal reception and transduction in response to extracellular cues,
    but also have roles in cellular and extracellular fluid motility
    \citep{brooks2014multiciliated, marshall2006cilia},
    for example, as the sperm flagellum.
    Consistent with their importance in cell signalling,
    defects in cilium formation (i.e. ciliogenesis) are associated with genetic disorders
    known collectively as ciliopathies, which can display
    neurological defects \citep{valente2014primary},
    skeletal abnormalities \citep{hammarsjo2017novel},
    and infertility \citep{inaba2016sperm} in addition to other phenotypes
    \citep{waters2011ciliopathies}.
    Many ciliopathies are associated with mutations in proteins that localize
    to the transition zone (TZ), the proximal-most region of the cilium which
    functions as a diffusion barrier and regulates the
    bi-directional transport of protein cargo at the base of the cilium
    \citep{reiter2012base, szymanska2012transition}.
    The TZ is essential for ciliogenesis and function.
    For example, the conserved TZ protein CEP290 is mutated in at least
    six different ciliopathies that lie on a spectrum of clinical features and severities,
    and is important for cilium formation
    and function in both humans \citep{shimada2017vitro, stowe2012centriolar}
    and Drosophila \citep{basiri2014migrating}.
    Although the protein composition of TZs has been investigated in various
    studies ranging from single gene analysis to proteomics,
    the process of maturation of the TZ, through which it is converted from a
    immature form to one competent at supporting
    cilium assembly, is relatively understudied.

    Ciliogenesis begins with the assembly of a nascent TZ at the tips of
    the basal body \citep{reiter2012base}.
    This nascent TZ undergoes maturation, during which its structure and protein
    composition changes, allowing for the
    establishment of a compartmentalized ciliary space bounded by the ciliary membrane
    and the TZ in which axoneme assembly and signalling can occur.
    The axoneme is a microtubule-based structure that forms the core of all cilia and flagella.
    In the Drosophila male germline, nascent TZs first assemble on basal bodies
    during early G2 phase in spermatocytes \citep{riparbelli2012assembly}.
    This occurs concomitantly with the anchoring of cilia to the plasma membrane,
    rearrangment of microtubules within the TZ \citep{gottardo2013cilium},
    and establishment of a
    ciliary membrane that will persist through meiosis
    \citep{riparbelli2012assembly} (Figure 1A).
    TZ maturation has been described in
    \textit{Paramecium} \citep{aubusson2015transition}
    \textit{Caenorhabditis elegans} \citep{serwas2017centrioles} and
    \textit{Drosophila melanogaster} \citep{gottardo2013cilium},
    and is most readily observed by an increase in TZ length
    in the Drosophila male germline.

    We previously showed that the membrane lipid phosphatidylinositol 4,5-bisphosphate
    (\PIP{}) is essential for the formation of the sperm flagellum in the Drosophila
    male germline \citep{wei2008depletion, fabian2010phosphatidylinositol}.
    \PIP{} is one of seven different phosphoinositides (PIPs) present in eukaryotes.
    It localizes primarily to the plasma membrane, where it is essential for
    modulation of actin cytoskeleton and vesicle trafficking amongst other things
    \citep{balla2013phosphoinositides}.
    \PIP{} has been linked to cilium function in many recent studies.
    The ciliary membrane has been shown to contain very little \PIP{} due to the action
    of the cilium resident lipid phosphatase INPP5E \citep{nakatsu2015phosphoinositide}.
    Inactivation of INPP5E leads to a build up of intraciliary \PIP{}
    which disrupts transport of certain signalling proteins in both vertebrates
    \citep{chavez2015modulation, garcia2015phosphoinositides, conduit2017compartmentalized}.
    and Drosophila \citep{park2015ciliary}.
    We sought to investigate the defects in axoneme assembly in Drosophila male germ cells
    with reduced \PIP{} 
    that we reported previously in light of the current understanding of the roles
    for \PIP{} in cilia as a modulator of cilium function.

    %
    %   Results - 1
    %
    \subsection{\PIP{} is essential for transition zone maturation}
    To investigate how the reduction of cellular \PIP{} affects ciliogenesis in the
    Drosophila male germline,
    we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
    under the spermatocyte-specific $\beta$2-tubulin promoter (referred to herein as \sigd{}),
    \citep{wei2008depletion}.
    Note that \sigd{} corresponds to ``SigD-high'' in \citep{fabian2010phosphatidylinositol}.
    SigD dephosphorylates \PIP{} \textit{in vivo},
    and we previously showed that \sigd{} induces male sterility
    due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
    To examine whether these were caused by aberrant TZ function,
    we examined the localization of fluorescently-tagged
    centriolar/basal body protein
    Ana1 (homolog of CEP295) \citep{goshima2007genes, blachon2009proximal}
    and the conserved TZ protein Cep290 \citep{basiri2014migrating}
    during early steps of cilium assembly in spermatocytes in both
    wild-type controls and \sigd{}.
    As shown in Figure 1,
    while Cep290 looks similar in control and \sigd{} in early G2 phase
    when TZs are still immature, 
    it grows to significantly longer lengths in \sigd{}
    compared to wild-type controls by the end of the G2 phase following
    the period of TZ maturation in spermatocytes.
    In contrast to the \textit{cep290} mutant, which contains
    longer than normal basal bodies \citep{basiri2014migrating},
    Ana1 length was not affected in \sigd{},
    and we did not observe a strong
    correlation between Cep290 and Ana1 lengths (Figure 1C).
    We previously showed that the structure of basal bodies
    from electron microscopy was normal, and that the centriolar
    markers GFP-PACT and Sas-4 \citep{basto2006flies}
    were normal when immunostained for
    in controls and \sigd{}.
    \citep{wei2008depletion}
    TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
    Mks1 \citep{vieillard2016transition}
    showed hyperelongation in \sigd{} (Figure 1D),
    suggesting that this phenotype is not specific to Cep290 but is shared
    by other members of the Drosophila TZ.
    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%
    in spermatocytes at late G2 phase)
    and showed high intra-cyst correlation (\textgreater 0.95) suggestive
    of a dosage-based response to a shared cellular factor,
    presumably SigD.
    Despite the persistence of hyperelongated TZs through meiosis,
    axonemes were able to
    elongate normally in post-meiotic cells (Figure 1E).
    However, as we showed previously, the ultrastructure of these axonemes
    was frequently aberrant,
    either lacking symmetry completely or containing triplet microtubules
    in addition to the usual doublets \citep{wei2008depletion}.

    %
    %   Results - 2
    %
    \subsection{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
    While \PIP{} is the major substrate for SigD in eukaryotic cells \textit{in vivo}
    \citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
    SigD can also dephosphorylate other PIPs \textit{in vitro}
    \citep{norris1998sopb}.
    To address whether TZ hyperelongation observed in \sigd{} represented a
    physiologically relevant phenotype in response to decreased \PIP{},
    we attempted to rescue it by
    co-expressing SigD with
    fluorescently-tagged full-length Skittles (Sktl)
    using the same $\beta$2-tubulin promoter.
    We found that Sktl expression was able to suppress TZ hyperelongation
    in a cilium-autonomous manner (Figure 2A and B).
    We also found that \textit{sktl} clones made
    using Flp/FRT-based mitotic recombination and expressing the
    basal body and TZ marker Unc
    \citep{baker2004mechanosensory, wei2008depletion}
    exhibited TZ hyperelongation (Figure 2C),
    suggesting that Sktl is important for TZ maturation.

   % Since Sktl expression suppressed TZ hyperelongation,
   % we investigated whether Sktl could localize to centrioles or cilia
   % in the Drosophila germline.
    Xu \textit{et al}. showed the vertebrate PIPKI$\gamma$ to be
    important for cilium formation in cultured cell lines
    \citep{xu2014pipkigamma}.
    As shown in Figure 2D, Drosophila PIPKIs arose from the recent duplication of
    the ancestral PIPKI gene,
    and are not orthologous to specific vertebrate PIPKI isoforms.
    Sktl has diverged more than its paralog PIP5K59B, and seems
    to be functionally related to PIPKI$\gamma$ in its roles at cilia,
    as well as the \textit{C. elegans} PPK-1 (See supplementary data in \citep{xu2014pipkigamma}).
    However, unlike the human PIPKI$\gamma$, which functions to license TZ assembly
    by promoting CP110 removal from basal bodies \citep{xu2016phosphatidylinositol},
    our results suggest that Sktl functions in
    regulating TZ length in the Drosophila male germline
    but not TZ assembly.
    Neither inactivation nor overexpression of \textit{cp110} affects
    cilium formation in Drosophila, and Cp110
    and is removed from basal bodies in the earliest stages of G2 phase in the male germline
    \citep{franz2013cp110}.

    %
    %   Results - 3
    %
    \subsection{Hyperelongated transition zones exhibit signs of functional defects}
    We sought to examine whether TZ hyperelongation due to SigD expression
    affected TZ function.
    During cell elongation following meiosis, the TZ detaches from
    the basal body and migrates along the growing axoneme, maintaining a ciliary compartment
    at the distal-most {\raise.17ex\hbox{$\scriptstyle\sim$}}5$\mu$m where tubulin
    is presumably incorporated into the axoneme
    \citep{basiri2014migrating, fabian2012drosophila}.
    We found that
    TZs that assembled in \sigd{} cells are non-migratory despite the growth of the
    axoneme (see Figure 1E) and the cell membrane, as shown by Unc and Cep290 localization
    (Figures 3A and 3B).
    We previously described ``comet-shaped'' localization of Unc-GFP in these cells,
    and we find that these hyperelongated Unc signals persist into cellular elongation
    despite elongation of the axoneme (Figure 3A, bottommost panel).

    In Drosophila and humans, basal bodies consist of microtubule triplets
    \citep{jana2016drosophila, lattao2017centrioles}
    while the axoneme contains microtubule doublets due to the obstruction of
    the C-tubule at the TZ \citep{gottardo2013cilium}.
    Consistent with a defect in the TZ barrier and the presence of
    microtubule triplets in axonemes in \sigd{} \citep{wei2008depletion},
    we observed that a subset of cilia (<5\%) in SigD-expressing cells
    contained puncta of Ana1, a core centriolar protein, at the tips
    of TZs marked with Cep290 (Figure 3C).
    We found that treatment of germ cells with Taxol as in \citep{riparbelli2013unique}
    could increase the penetrance of this phenotype from <5\% in untreated cells
    to \textgreater25\% in cells treated with 4 $\mu$M Taxol (Figure 3D)
    without affecting Cep290 length significantly (Figure 3E).
    Taxol treatment stabilizes microtubules and is thought to disrupt TZ maturation
    by inhibiting microtubule rearrangements \citep{riparbelli2012assembly}.
    Taxol treatment alone did not induce this phenotype in wild-type controls in our hands
    at varying concentrations ($p$ <0.01 at 5\% penetrance).
    Triplet microtubules within the axoneme are also observed in Taxol-treated cells
    \citep{riparbelli2013unique}, further supporting a relationship between
    \PIP{} and microtubule reorganization in TZ maturation.
    Asterless (homolog of CEP152), another centriolar protein,
    did not localize to TZ-distal puncta in \sigd{}
    \citep{dzhindzhev2010asterless, blachon2008drosophila} ($p$ <0.01)
    suggesting that these TZ-distal
    sites are not fully centriolar in protein composition.

    %
    %   Results - 4
    %
    \subsection{The \textit{onion rings} mutant decouples defects found in cells with reduced levels of \PIP{}}
    We previously showed that male flies homozygous for the \textit{onion rings}
    (\textit{onr}) mutant of Drosophila Exo84 were sterile, and had phenotypes
    similar to \sigd{} such as defects in cell polarity \citep{wei2008depletion}.
    Exo84 is a component of the octameric exocyst complex, which binds
    \PIP{} and regulates membrane trafficking at the plasma membrane.
    To investigate whether defects in TZ hyperelongation could be explained by
    defective Exo84 function, we examined TZs in \textit{onr} mutants.
    We found that the \textit{onr} mutant did not display hyperelongated TZs (Figure 4C),
    suggesting that Exo84 is dispensable for TZ maturation.

    Due to the involvement of exocyst in membrane trafficking at the plasma membrane,
    we examined whether cilium-associated membrane dynamics were affected in \sigd{}
    or \textit{onr} mutants similar to \textit{dila; cby} mutants
    \citep{vieillard2016transition}.
    We found that while TZs in \sigd{} and \textit{onr} cells anchored properly
    to the plasma membrane, they were unable to either establish or maintain
    membrane connections, and were rendered cytoplasmic (Figure 4A and B) similar to
    \textit{dila; cby} mutants.
    Although we were not able to determine the localization of Exo84 due to the
    lack of available reagents,
    we found that GFP-tagged Exo70 localized to centrioles (Figure 4D).
    Exo70 can directly bind to \PIP{} and mediates the recruitment of
    the exocyst complex to the plasma membrane \citep{he2007exo70}.
    Our results suggest that exocyst regulates
    cilium-membrane associations similar to \PIP{}, and that TZ hyperelongation and loss of
    membrane-cilium association are genetically separable phenotypes.

    \section{Discussion}
    The process of maturation of a TZ from a nascent form to a fully functional one,
    leading ultimately to axoneme assembly and ciliary signalling,
    requires orchestration of various proteins and cellular pathways
    \citep{reiter2012base}.
    In the Drosophila male germline, TZ maturation occurs during the
    extended G2 phase in spermatocytes prior to meiosis, and can be readily
    observed by an increase in TZ length using fluorescence microscopy.
    Our results suggest that normal execution of this process
    requires \PIP{}, and that depletion of \PIP{} induces TZs to
    grow longer than normal.
    Regulation of TZ length in the Drosophila male germline has been reported
    previously.
    For example, \textit{mks1} mutants have shorter TZs \citep{pratt2016drosophila},
    while
    \textit{cby; dila} and \textit{cby} mutants display hyperelongated ones
    \citep{enjolras2012drosophila,vieillard2016transition}.
    Since both Cby and Mks1 are hyperelongated in \sigd{} cells,
    \PIP{} seems to be intimately involved in this process as well but it does
    so independantly of Cby and Mks1.

    The majority of \PIP{} at the plasma membrane is produced by PIPKIs
    \citep{balla2013phosphoinositides, hammond2012pi4p}
    and these seem to have a conserved role at cilia.
    In this study, we showed that mutation of the PIPKI Skittles (Sktl)
    induced hyperelongated TZs, similar to SigD expression.
    We were able rescue TZ hyperelongation by expression of full-length Sktl to
    a large degree.
    Interestingly, some cells showed cilium-autonomous suppression of lengths.
    Since the development of the Drosophila male germline occurs in syncytial ``cysts''
    of cells which share the same cytoplasm,
    cilium-autonomous rescue suggests that Skittles might function \textit{in situ}
    to regulate TZ maturation in these cells.
    In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
    syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy.
    The recent discovery of the role of LCCS1-associated GLE1 protein in cilium
    function \citep{jao2017role} further supports this hypothesis.
    This is further evidence that PIPKIs might represent ciliopathy-associated genes
    or genetic modifiers of disease, as previously hypothesized
    \citep{xu2016phosphatidylinositol}.

>>>>

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
%\usepackage[charter]{mathdesign} % I hate how charter greeks look
\usepackage[numbers]{natbib}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{lineno}
\usepackage{setspace}
\usepackage{microtype}
\graphicspath{{../figures/}}
\bibliographystyle{unsrtcurrbiol}

@@

% newcommand
\newcommand{\PIP}{PIP\textsubscript{2}}
\newcommand{\sigd}{$\beta$\textsubscript{2}t-SigD}
\newcommand{\sktl}{\textit{sktl}}
\makeatletter
\renewcommand\@biblabel[1]{#1.}
\makeatother

@@

\title{\vspace{-1cm} \bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}}
\author[1,2]{Alind Gupta \thanks{\url{alind.gupta@mail.utoronto.ca}}}
\author[2]{Lacramioara Fabian \thanks{\url{lacramioara.fabian@sickkids.ca}}}
\author[1,2]{Julie A. Brill \thanks{\url{julie.brill@sickkids.ca} (Corresponding author)}}

\affil[1]{\small Department of Molecular Genetics, University of Toronto, Toronto, ON M5S 1A8, Canada}
\affil[2]{\small Program in Cell Biology, Hospital for Sick Children, Toronto, ON M5G 1X8, Canada}
\date{}

@@

\maketitle
\raggedbottom

@@

    \section{Results}
    Cilia are sensory organelles that are present on almost all cells in the human body
    \citep{satir2010primary, marshall2006cilia}.
    They function in signal reception and transduction in response to extracellular cues,
    but also have roles in cellular and extracellular fluid motility
    \citep{brooks2014multiciliated, marshall2006cilia},
    for example, as the sperm flagellum.
    Consistent with their importance in cell signalling,
    defects in cilium formation (i.e. ciliogenesis) are associated with genetic disorders
    known collectively as ciliopathies, which can display
    neurological defects \citep{valente2014primary},
    skeletal abnormalities \citep{hammarsjo2017novel},
    and infertility \citep{inaba2016sperm}, in addition to other phenotypes
    \citep{waters2011ciliopathies}.
    Many ciliopathies are associated with mutations in proteins that localize
    to the transition zone (TZ), the proximal-most region of the cilium that
    functions as a diffusion barrier and regulates the
    bidirectional transport of protein cargo at the base of the cilium
    \citep{reiter2012base, szymanska2012transition}.
    The TZ is essential for ciliogenesis and function.
    For example, the conserved TZ protein CEP290 is mutated in at least
    six different ciliopathies that lie on a spectrum of clinical features and severities
    and is important for cilium formation
    and function in both humans \citep{shimada2017vitro, stowe2012centriolar}
    and Drosophila \citep{basiri2014migrating}.
    Although the protein composition of TZs has been investigated in various
    studies ranging from single gene analysis to proteomics,
    the process of maturation of the TZ, through which it is converted from an
    immature form to one competent at supporting
    cilium assembly, is relatively understudied.

    Ciliogenesis begins with assembly of a nascent TZ at the tip of
    the basal body \citep{reiter2012base}.
    This nascent TZ undergoes maturation, during which its structure and protein
    composition changes, allowing for the
    establishment of a compartmentalized ciliary space, bounded by the ciliary membrane
    and the TZ, in which axoneme assembly and signalling can occur.
    The axoneme is a microtubule-based structure that forms the core of all cilia and flagella.
    In the Drosophila male germline, nascent TZs first assemble on basal bodies
    during early G2 phase in spermatocytes \citep{riparbelli2012assembly}.
    This occurs concomitantly with anchoring of cilia to the plasma membrane,
    rearrangment of microtubules within the TZ \citep{gottardo2013cilium},
    and establishment of a
    ciliary membrane that will persist through meiosis
    \citep{riparbelli2012assembly} (Figure 1A).
    TZ maturation has been described in
    \textit{Paramecium} \citep{aubusson2015transition},
    \textit{Caenorhabditis elegans} \citep{serwas2017centrioles} and
    \textit{Drosophila melanogaster} \citep{gottardo2013cilium},
    and is most readily observed by an increase in TZ length
    in the Drosophila male germline.

    We previously showed that the membrane lipid phosphatidylinositol 4,5-bisphosphate
    (\PIP{}) is essential for formation of the sperm flagellum in the Drosophila
    male germline \citep{wei2008depletion, fabian2010phosphatidylinositol}.
    \PIP{} is one of seven different phosphoinositides (PIPs) present in eukaryotes.
    It localizes primarily to the plasma membrane, where it is essential for
    modulation of the actin cytoskeleton and vesicle trafficking, as well as numerous
    other processes \citep{balla2013phosphoinositides}.
    \PIP{} has been linked to cilium function in recent studies.
    While the ciliary membrane has been found to contain very little \PIP{} due to the action
    of the cilium resident PIP phosphatase INPP5E,
    the base of the cilium is enriched in \PIP{}
    \citep{nakatsu2015phosphoinositide}.
    Inactivation of INPP5E leads to a build up of intraciliary \PIP{},
    which disrupts transport of components of the Hedgehog signalling pathway in vertebrates
    \citep{chavez2015modulation, garcia2015phosphoinositides, conduit2017compartmentalized}
    and ion channels involved in mechanotransduction in Drosophila \citep{park2015ciliary}.
    In light of this current understanding of the role
    for \PIP{} as a modulator of cilium function,
    we sought to investigate the cause of defects in axoneme assembly in Drosophila male germ cells
    with reduced levels of \PIP{} from \citep{wei2008depletion}.

    %
    %   Results - 1
    %
    \subsection{\PIP{} is essential for transition zone maturation}
    To investigate how reduction of cellular \PIP{} affects ciliogenesis in the
    Drosophila male germline,
    we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
    under the control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter (referred to herein as \sigd{}),
    \citep{wei2008depletion}.
    Note that \sigd{} corresponds to ``SigD-high'' in \citep{fabian2010phosphatidylinositol}.
    SigD dephosphorylates \PIP{} \textit{in vivo},
    and we previously showed that \sigd{} induces male sterility
    due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
    To examine whether these defects were caused by aberrant TZ function,
    we examined the localization of fluorescently-tagged versions of the
    centriolar/basal body protein
    Ana1 (homolog of CEP295) \citep{goshima2007genes, blachon2009proximal}
    and the conserved TZ protein Cep290 \citep{basiri2014migrating}
    during early steps of cilium assembly in spermatocytes.
    Cep290 distribution appeared similar in control and \sigd{} in early G2 phase
    when TZs are still immature.
    In contrast, Cep290-labelled TZs were significantly longer in \sigd{}
    compared to wild-type controls by the end of the G2 phase following
    the period of TZ maturation in spermatocytes (Figure 1B and 1C).
    Unlike Drosophila \textit{cep290} mutants, which contain
    longer than normal basal bodies \citep{basiri2014migrating},
    Ana1 length was not affected in \sigd{},
    and we did not observe a strong
    correlation between Cep290 and Ana1 lengths (Figure 1C).
    We previously showed that the structure of basal bodies
    from electron microscopy is normal, and that the localization of the centriolar
    marker GFP-PACT \citep{basto2006flies}
    is similar in controls and \sigd{} \citep{wei2008depletion}.
    In contrast, TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
    Mks1 \citep{vieillard2016transition}
    exhibited hyperelongation in \sigd{} (Figure 1D),
    suggesting that this phenotype is not specific to Cep290 but is shared
    by other members of the Drosophila TZ.
    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%
    in spermatocytes at late G2 phase)
    and showed high intra-cyst correlation (\textgreater 0.95) suggestive
    of a dosage-based response to a shared cellular factor,
    presumably SigD.
    Despite the persistence of hyperelongated TZs through meiosis,
    axonemes, visualized by staining for acetylated tubulin, were able to
    elongate normally in post-meiotic cells (Figure 1E).
    However, as we showed previously, the ultrastructure of these axonemes
    is frequently aberrant,
    either lacking symmetry completely or containing triplet microtubules
    in addition to the usual doublets \citep{wei2008depletion}.

    %
    %   Results - 2
    %
    \subsection{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
    Whereas \PIP{} is the major substrate for SigD in eukaryotic cells \textit{in vivo}
    \citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
    SigD can also dephosphorylate other PIPs \textit{in vitro}
    \citep{norris1998sopb}.
    To address whether TZ hyperelongation observed in \sigd{} represented a
    physiologically relevant phenotype in response to decreased \PIP{},
    we attempted to rescue the TZ phenotype by
    co-expressing \sigd{} with
    fluorescently-tagged Skittles (Sktl)
    using the same $\beta$\textsubscript{2}-tubulin promoter.
    We found that Sktl expression was able to suppress TZ hyperelongation
    in a cilium-autonomous manner (Figure 2A and B).
    We also found that \textit{sktl} clones made
    using Flp/FRT-based mitotic recombination and expressing the
    basal body and TZ marker Unc
    \citep{baker2004mechanosensory, wei2008depletion}
    exhibited TZ hyperelongation (Figure 2C),
    suggesting that Sktl is important for TZ maturation.

    A previous report showed the vertebrate PIPKI$\gamma$ to be
    important for cilium formation in cultured cell lines
    \citep{xu2014pipkigamma}.
    Drosophila PIPKIs arose from the recent duplication of
    the ancestral PIPKI gene,
    and are not orthologous to specific vertebrate PIPKI isoforms (Figure 2D).
    Sktl has diverged more than its paralog PIP5K59B, and seems
    to be functionally related to PIPKI$\gamma$
    and the \textit{C. elegans} PPK-1 in having roles at cilia \citep{xu2014pipkigamma}.
    However, unlike the human PIPKI$\gamma$, which licenses TZ assembly
    by promoting CP110 removal from basal bodies \citep{xu2016phosphatidylinositol},
    our results suggest that Sktl functions in
    regulating TZ length in the Drosophila male germline,
    but not TZ assembly. 
    Notably, neither inactivation nor overexpression of \textit{cp110} affects
    cilium formation in Drosophila, and Cp110
    and is removed from basal bodies in the earliest stages of G2 phase in the Drosophila male germline
    \citep{franz2013cp110}.

    %
    %   Results - 3
    %
    \subsection{Hyperelongated transition zones exhibit signs of functional defects}
    We sought to examine whether TZ hyperelongation due to SigD expression
    affected TZ function.
    During cell elongation following meiosis, the TZ detaches from
    the basal body and migrates along the growing axoneme, maintaining a ciliary compartment
    at the distal-most {\raise.17ex\hbox{$\scriptstyle\sim$}}5$\mu$m where tubulin
    is presumably incorporated into the axoneme
    \citep{basiri2014migrating, fabian2012drosophila}.
    As shown by Unc and Cep290 localization,
    TZs that assembled in \sigd{} cells were frequently incapable of detaching from
    the basal body and migrating along the axoneme despite
    axoneme elongation (Figure 1E) and cellular elongation
    (Figures 3A and 3B).
    We previously described ``comet-shaped'' localization of Unc-GFP in these cells,
    and we find that these hyperelongated Unc signals persist during cellular elongation
    despite elongation of the axoneme (Figure 3A bottommost panel and Figure 1E).

    In Drosophila and humans, basal bodies consist of microtubule triplets
    \citep{jana2016drosophila, lattao2017centrioles},
    whereas the axoneme contains microtubule doublets due to obstruction of
    the C-tubule at the TZ \citep{gottardo2013cilium}.
    Consistent with a defect in the TZ barrier and the presence of
    microtubule triplets in axonemes in \sigd{} \citep{wei2008depletion},
    we observed that a subset of cilia (<5\%) in SigD-expressing cells
    contained puncta of Ana1, a core centriolar protein, at the tips
    of TZs marked with Cep290 (Figure 3C).
    We found that treatment of germ cells with Taxol, as in \citep{riparbelli2013unique},
    could increase the penetrance of this phenotype from <5\% in untreated cells
    to \textgreater25\% in cells treated with 4 $\mu$M Taxol (Figure 3D)
    without affecting Cep290 length significantly (Figure 3E).
    Taxol treatment stabilizes microtubules and is thought to disrupt TZ maturation
    by inhibiting microtubule rearrangements \citep{riparbelli2012assembly}.
    Taxol treatment alone did not induce this phenotype in wild-type controls in our hands
    at varying concentrations ($p$ <0.01 at 5\% penetrance).
    Triplet microtubules within the axoneme are also observed in Taxol-treated cells
    \citep{riparbelli2013unique}, further supporting a relationship between
    \PIP{} and microtubule reorganization in TZ maturation.
    Fluorescently-tagged Asterless (homolog of CEP152), a pericentriolar protein
    \citep{blachon2008drosophila, dzhindzhev2010asterless},
    did not localize to TZ-distal puncta in \sigd{} ($p$ <0.01)
    suggesting that these TZ-distal
    sites are not fully centriolar in protein composition.

    %
    %   Results - 4
    %
    \subsection{The \textit{onion rings} mutant decouples defects found in cells with reduced levels of \PIP{}}
    We previously showed that male flies homozygous for the \textit{onion rings}
    (\textit{onr}) mutant of Drosophila Exo84 were sterile, and had phenotypes
    similar to \sigd{} such as defects in cell polarity \citep{wei2008depletion}.
    Exo84 is a component of the octameric exocyst complex, which binds
    \PIP{} and regulates membrane trafficking at the plasma membrane.
    To investigate whether defects in TZ hyperelongation could be explained by
    defective Exo84 function, we examined TZs in \textit{onr} mutants.
    Unlike \sigd{}, the \textit{onr} mutant did not display hyperelongated TZs (Figure 4C),
    suggesting that Exo84 is dispensable for TZ maturation.

    Due to involvement of exocyst in membrane trafficking at the plasma membrane,
    we examined whether cilium-associated membranes were affected in \sigd{}
    or \textit{onr} mutants in a manner similar to \textit{dila; cby} mutants
    \citep{vieillard2016transition}.
    Whereas TZs in \sigd{} and \textit{onr} cells anchored properly
    to the plasma membrane, they were unable to either establish or maintain
    membrane connections, and were rendered cytoplasmic (Figure 4A and B) similar to
    \textit{dila; cby} mutants.
    Although we were not able to determine the localization of Exo84 due to the
    lack of available reagents,
    we found that GFP-tagged Exo70 localized to centrioles (Figure 4D).
    Exo70 can directly bind to \PIP{} and mediates the recruitment of
    the exocyst complex to the plasma membrane \citep{he2007exo70}.
    Our results suggest that the exocyst, and Exo84 in particular, regulates
    cilium-membrane associations, similar to \PIP{}, and that TZ hyperelongation and loss of
    membrane-cilium association are genetically separable phenotypes.

    \section{Discussion}
    The process of maturation of a TZ from a nascent form to a fully functional one,
    leading ultimately to axoneme assembly and ciliary signalling,
    requires orchestration of various proteins and cellular pathways
    \citep{reiter2012base}.
    In the Drosophila male germline, TZ maturation occurs during the
    extended G2 phase in spermatocytes prior to meiosis, and can be readily
    observed by an increase in TZ length using fluorescence microscopy.
    Our results suggest that normal execution of this process
    requires \PIP{}, and that depletion of \PIP{} induces TZs to
    grow longer than normal.
    Regulation of TZ length in the Drosophila male germline has been reported
    previously.
    For example, \textit{mks1} mutants have shorter TZs \citep{pratt2016drosophila},
    whereas
    \textit{cby; dila} and \textit{cby} mutants display hyperelongated TZs
    \citep{enjolras2012drosophila,vieillard2016transition}.
    Since both Cby and Mks1 are hyperelongated in \sigd{} cells,
    \PIP{} seems to be intimately involved in this process as well, but it does
    so independantly of Cby and Mks1.

    The majority of \PIP{} at the plasma membrane is produced by PIPKIs
    \citep{balla2013phosphoinositides, hammond2012pi4p}
    and these seem to have a conserved role at cilia.
    In this study, we showed that mutation of the PIPKI Skittles (Sktl)
    induced hyperelongated TZs, similar to SigD expression.
    We were able rescue TZ hyperelongation in \sigd{} by expression of full-length Sktl.
    Interestingly, some cells showed cilium-autonomous suppression of TZ length.
    Because the development of the Drosophila male germline occurs in syncytial cysts
    of cells that share the same cytoplasm,
    cilium-autonomous rescue suggests Skittles might function \textit{in situ}
    to regulate TZ maturation in these cells.
    In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
    syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy.
    The recent discovery of the role of LCCS1-associated GLE1 protein in cilium
    function \citep{jao2017role} further supports this hypothesis.
    Our data support the idea that PIPKIs might represent ciliopathy-associated genes
    or genetic modifiers of disease, as previously postulated
    \citep{xu2016phosphatidylinositol}.

    In this study, we report two phenotypes associated with
    hyperelongated TZs that we postulate to be indicators of
    TZ dysfunction.
    Firstly, we show that hyperelongated TZs are unable to
    detach from basal bodies at the onset of axoneme elongation
    in spermatids, unlike TZs in normal cells \citep{basiri2014migrating, fabian2012drosophila}.
    Nonetheless, axonemes can assemble despite the lack of a functional
    TZ or membrane association in \sigd{} cells.
    As we previously reported, these axonemes frequently exhibit aberrant
    ultrastructure \citep{wei2008depletion}.
    This is similar to \textit{cep290} \citep{basiri2014migrating}
    and \textit{dila}; \textit{cby} \citep{vieillard2016transition}
    mutants,
    which can assemble spermatid axonemes despite lacking
    functional TZs.
